Conceptualizing open health data platforms for low- and middle income countries

### 2024-05-12 index.tex
Update render

\caption{\label{tbl-digital-public-goods}Overview of current open source
implementations of components included in the OpenHIE specification that
are FHIR-compatible. The category Analytics Services is not a part of
the original OpenHIE and is discussed in the paper. Point-of-Service
systems are excluded for brevity. A systematic review of such digital
public goods is beyond the scope of this document.}

\includegraphics{images/digital-public-goods.png}

>>>>

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2558}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2558}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4884}}@{}}
\caption{Overview of current open source implementations of components
included in the OpenHIE specification that are FHIR-compatible. The
category Analytics Services is not a part of the original OpenHIE and is
discussed in the paper. Point-of-Service systems are excluded for
brevity. A systematic review of such digital public goods is beyond the
scope of this document.}\label{tbl-digital-public-goods}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Category
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Component
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Digital Public Good
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Category
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Component
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Digital Public Good
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\textbf{Interoperability layer (IOL)} & IOL &
\href{http://openhim.org}{OpenHIM} \\
\textbf{Registry Services} & Client Registry (CR) &
\href{https://help.santesuite.org/product-overview/santesuite-products/master-patient-index-santempi}{SanteMPI} \\
& & \href{https://jembi.gitbook.io/jempi/}{JeMPI} \\
& & \href{https://www.openclientregistry.org/}{OpenCR} \\
& Facility Registry (FR) &
\href{https://github.com/intrahealth/gofr}{Global Open Facility Registry
(GOFR)} \\
& Health Worker Registry (HWR) &
\href{https://www.ihris.org/ihris-50}{iHRIS} \\
& Terminology Service (TS) &
\href{https://openconceptlab.org/terminology-service/}{OCL Terminology
Service} \\
& Product Catalog (PC) & not available \\
\textbf{Business Domain Services} & Shared Health Record (SHR) &
\href{https://hapifhir.io/}{HAPI FHIR} \\
& & \href{https://www.health-samurai.io/fhirbase}{Fhirbase} \\
& & \href{https://github.com/microsoft/fhir-server}{FHIR Server for
Azure} \\
& & \href{https://github.com/I-TECH-UW/shared-health-record}{I-TECH-UW
SHR} \\
& Health Management Information System (HMIS) &
\href{http://dhis2.org/}{DHIS2} \\
& Finance and Insurance Service (FIS) &
\href{http://openimis.org/}{OpenIMIS} \\
& Logistics Management Information System (LMIS) &
\href{http://openlmis.org/}{OpenLMIS} \\
\textbf{Generic} & Identity and Access Management (IAM) &
\href{https://www.keycloak.org/}{Keycloak} \\
& Gateway \& proxy & \href{https://github.com/google/fhir-gateway}{FHIR
Information Gateway} \\
& Admin dashboard for SHR &
\href{https://github.com/onaio/fhir-web}{OpenSRP FHIR Web} \\
& Configuration and deployment &
\href{https://jembi.gitbook.io/instant-v2/}{Instant OpenHIE} \\
\end{longtable}
